---
title: "Dashboard"
format: dashboard
---

```{r}
#| label: setup
#| message: false
#| warning: false

library(tidyverse)
library(scales)
```

```{r}
#| label: prepare-data

marketing_data <- tibble(
  platform = c(
    "Instagram", "Instagram", "Instagram",
    "TikTok", "TikTok", "TikTok",
    "Email", "Email", "Email",
    "YouTube", "YouTube", "YouTube"
  ),
  campaign = c(
    "Awareness", "Engagement", "Conversion",
    "Awareness", "Engagement", "Conversion",
    "Awareness", "Engagement", "Conversion",
    "Awareness", "Engagement", "Conversion"
  ),
  impressions = c(
    12000, 15000, 9000,
    18000, 22000, 14000,
    7000, 8500, 6500,
    10000, 12000, 9500
  ),
  clicks = c(
    720, 1050, 810,
    1260, 1760, 1540,
    630, 765, 780,
    700, 960, 855
  ),
  conversions = c(
    72, 95, 130,
    90, 140, 210,
    84, 102, 156,
    65, 88, 125
  ),
  spend = c(
    900, 1100, 1300,
    1000, 1500, 1800,
    400, 450, 600,
    800, 950, 1200
  )
)

marketing_summary <- marketing_data |>
  mutate(
    ctr = clicks / impressions,
    conversion_rate = conversions / clicks,
    cost_per_conversion = spend / conversions
  )
```

# Overview

## Key Metrics

```{r}
#| content: valuebox
#| title: "Total Impressions"
#| icon: eye
#| color: primary

list(value = comma(sum(marketing_summary$impressions)))
```

```{r}
#| content: valuebox
#| title: "Total Clicks"
#| icon: cursor
#| color: success

list(value = comma(sum(marketing_summary$clicks)))
```

```{r}
#| content: valuebox
#| title: "Total Conversions"
#| icon: graph-up-arrow
#| color: warning

list(value = comma(sum(marketing_summary$conversions)))
```

## Platform Performance

```{r}
#| title: "Conversions by Platform"

marketing_summary |>
  group_by(platform) |>
  summarize(total_conversions = sum(conversions), .groups = "drop") |>
  ggplot(aes(x = reorder(platform, total_conversions), y = total_conversions)) +
  geom_col() +
  coord_flip() +
  labs(
    x = "Platform",
    y = "Conversions",
    title = "Total Conversions by Platform"
  ) +
  theme_minimal()
```

```{r}
#| title: "Cost per Conversion by Platform"

marketing_summary |>
  group_by(platform) |>
  summarize(cost_per_conversion = sum(spend) / sum(conversions), .groups = "drop") |>
  ggplot(aes(x = reorder(platform, cost_per_conversion), y = cost_per_conversion)) +
  geom_col() +
  coord_flip() +
  labs(
    x = "Platform",
    y = "Cost per Conversion",
    title = "Cost per Conversion by Platform"
  ) +
  theme_minimal()
```

# Campaign Performance

## Campaign Metrics

```{r}
#| title: "Click-Through Rate by Campaign"

marketing_summary |>
  group_by(campaign) |>
  summarize(ctr = sum(clicks) / sum(impressions), .groups = "drop") |>
  ggplot(aes(x = campaign, y = ctr)) +
  geom_col() +
  scale_y_continuous(labels = percent) +
  labs(
    x = "Campaign Type",
    y = "Click-Through Rate",
    title = "Click-Through Rate by Campaign"
  ) +
  theme_minimal()
```

```{r}
#| title: "Conversion Rate by Campaign"

marketing_summary |>
  group_by(campaign) |>
  summarize(conversion_rate = sum(conversions) / sum(clicks), .groups = "drop") |>
  ggplot(aes(x = campaign, y = conversion_rate)) +
  geom_col() +
  scale_y_continuous(labels = percent) +
  labs(
    x = "Campaign Type",
    y = "Conversion Rate",
    title = "Conversion Rate by Campaign"
  ) +
  theme_minimal()
```

# Data Notes

This dashboard uses a small sample marketing dataset created for this assignment. The purpose is to demonstrate how Quarto dashboards can organize key metrics, charts, and audience-facing insights in a clear format.

The dashboard focuses on common marketing performance indicators, including impressions, clicks, conversions, click-through rate, conversion rate, and cost per conversion.

