---
title: "Streaming Service Loyalty Dashboard"
format: dashboard
---

```{r}
#| label: setup
#| message: false
#| warning: false

library(tidyverse)
library(readxl)
library(scales)
```

```{r}
#| label: load-data

survey_raw <- read_excel(
  "data/streaming-survey-cleaned.xlsx",
  sheet = "Analysis Data"
)

survey_data <- survey_raw |>
  filter(ResponseId != "Response ID") |>
  mutate(
    loyalty_index = as.numeric(`Loyalty Index`),
    nps_score = as.numeric(Q4),
    nps_category = `NPS Category`,
    cancellation_risk = `Cancellation Risk`,
    cancelled_last_year = `Cancelled A Service Within The Last Year`,
    keep_using = as.numeric(Q3_1),
    first_choice = as.numeric(Q3_2),
    recommend = as.numeric(Q3_3),
    not_switch = as.numeric(Q3_4),
    trust = as.numeric(Q3_5),
    cancellation_likelihood = as.numeric(Q6)
  )

valid_responses <- nrow(survey_data)

mean_loyalty <- mean(survey_data$loyalty_index, na.rm = TRUE)

high_risk_pct <- survey_data |>
  summarize(value = mean(cancellation_risk == "High risk", na.rm = TRUE)) |>
  pull(value)

cancelled_pct <- survey_data |>
  summarize(value = mean(cancelled_last_year == "Yes", na.rm = TRUE)) |>
  pull(value)

avg_nps <- mean(survey_data$nps_score, na.rm = TRUE)
```

# Overview

## Key Metrics

```{r}
#| content: valuebox
#| title: "Valid Responses"
#| icon: people
#| color: primary

list(value = comma(valid_responses))
```

```{r}
#| content: valuebox
#| title: "Mean Loyalty Index"
#| icon: star
#| color: success

list(value = number(mean_loyalty, accuracy = 0.01))
```

```{r}
#| content: valuebox
#| title: "High Cancellation Risk"
#| icon: exclamation-triangle
#| color: warning

list(value = percent(high_risk_pct, accuracy = 1))
```

```{r}
#| content: valuebox
#| title: "Cancelled Last Year"
#| icon: x-circle
#| color: danger

list(value = percent(cancelled_pct, accuracy = 1))
```

## Loyalty and Risk

```{r}
#| title: "NPS Category Breakdown"

survey_data |>
  filter(!is.na(nps_category)) |>
  count(nps_category) |>
  ggplot(aes(x = reorder(nps_category, n), y = n)) +
  geom_col() +
  coord_flip() +
  labs(
    x = "NPS Category",
    y = "Number of Respondents",
    title = "NPS Category Breakdown"
  ) +
  theme_minimal()
```

```{r}
#| title: "Cancellation Risk Breakdown"

survey_data |>
  filter(!is.na(cancellation_risk)) |>
  count(cancellation_risk) |>
  ggplot(aes(x = reorder(cancellation_risk, n), y = n)) +
  geom_col() +
  coord_flip() +
  labs(
    x = "Cancellation Risk",
    y = "Number of Respondents",
    title = "Cancellation Risk Breakdown"
  ) +
  theme_minimal()
```

# Loyalty Drivers

## Loyalty Statement Averages

```{r}
#| title: "Average Ratings for Loyalty Statements"

loyalty_statement_data <- survey_data |>
  summarize(
    `Intend to keep using` = mean(keep_using, na.rm = TRUE),
    `One of my first choices` = mean(first_choice, na.rm = TRUE),
    `Would recommend` = mean(recommend, na.rm = TRUE),
    `Would not easily switch` = mean(not_switch, na.rm = TRUE),
    `Trust the service` = mean(trust, na.rm = TRUE)
  ) |>
  pivot_longer(
    cols = everything(),
    names_to = "statement",
    values_to = "average_rating"
  )

loyalty_statement_data |>
  ggplot(aes(x = reorder(statement, average_rating), y = average_rating)) +
  geom_col() +
  coord_flip() +
  scale_y_continuous(limits = c(0, 5)) +
  labs(
    x = "Loyalty Statement",
    y = "Average Rating",
    title = "Average Ratings for Loyalty Statements"
  ) +
  theme_minimal()
```

```{r}
#| title: "Loyalty Index by Cancellation History"

survey_data |>
  filter(!is.na(cancelled_last_year), !is.na(loyalty_index)) |>
  ggplot(aes(x = cancelled_last_year, y = loyalty_index)) +
  geom_boxplot() +
  scale_y_continuous(limits = c(0, 5)) +
  labs(
    x = "Cancelled a Streaming Service Within the Past Year",
    y = "Loyalty Index",
    title = "Loyalty Index by Cancellation History"
  ) +
  theme_minimal()
```

# Cancellation Behavior

## Risk and Retention

```{r}
#| title: "Cancellation Risk by Past Cancellation"

survey_data |>
  filter(!is.na(cancelled_last_year), !is.na(cancellation_risk)) |>
  count(cancelled_last_year, cancellation_risk) |>
  group_by(cancelled_last_year) |>
  mutate(percent = n / sum(n)) |>
  ggplot(aes(x = cancelled_last_year, y = percent, fill = cancellation_risk)) +
  geom_col(position = "fill") +
  scale_y_continuous(labels = percent_format()) +
  labs(
    x = "Cancelled a Streaming Service Within the Past Year",
    y = "Percent of Respondents",
    fill = "Cancellation Risk",
    title = "Cancellation Risk by Past Cancellation"
  ) +
  theme_minimal()
```

```{r}
#| title: "Cancellation Likelihood Distribution"

survey_data |>
  filter(!is.na(cancellation_likelihood)) |>
  count(cancellation_likelihood) |>
  ggplot(aes(x = factor(cancellation_likelihood), y = n)) +
  geom_col() +
  labs(
    x = "Likelihood of Canceling in the Next 6 Months",
    y = "Number of Respondents",
    title = "Cancellation Likelihood Distribution"
  ) +
  theme_minimal()
```

# Data Notes

This dashboard uses survey data from the Streaming Service Loyalty research project. The purpose of the dashboard is to summarize loyalty, recommendation behavior, and cancellation risk among streaming service consumers.

The dashboard focuses on key indicators such as loyalty index, NPS category, cancellation risk, and whether respondents canceled a streaming service within the past year.

Because the survey sample is small, the results should be interpreted as exploratory rather than representative of the entire streaming market.

